---
title: "p8105_hw1_iho2104"
author: "Ixtaccihuatl Obregon"
date: "2023-09-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(moderndive)
library(tidyverse)
library(ggplot2)
```

# Problem One 

The data

```{r}
data("early_january_weather")
view(early_january_weather)
```

Row, Columns, and Mean of the Data

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
early_january_weather %>% 
  pull(temp) %>% 
  mean()
```

The variables in this dataset are origin, year, month, day, hour, temp, dew point, humidity, wind, and wind speed, etc. 

The size of the dataset is 358 x 15. 

The mean temperature was about 39.58

Scatterplot of time vs temp 

```{r}
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp)) + geom_point(aes(colour=humid))
```

The scatterplot shows the hourly change in temperature, meaning the day-night temp cycle is shown. Temperature rises from Jan 07 to Jan 14, with higher temperature having a higher humidity point.

Save plot with ggsave

```{r}
ggsave("early_january_weather.pdf")
```

# Problem Two

Random sample of size 10 from a standard normal distribution 

```{r}
sample = rnorm(1:10)
view(sample)
```

Logical vector indicating whether elements of the sample are greater than 0 

```{r}
any(sample>0)
```

A character vector of length 10 

```{r}
sentence = c("Today", "will", "be", "an", "easy","fun", "and", "productive", "Friday", "morning")
```

A factor vector of length 10, with 3 different factor "levels

```{r}
coffee = factor(c("iced", "iced", "hot", "frap", "hot", "iced", "hot", "frap", "iced", "iced"),
                levels = c("iced", "hot", "frap"))
length(coffee)
```



